The function-sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-25 crelle-dictionary.tex
New abstract, again.

\begin{abstract}
We extend the function-sheaf dictionary to smooth commutative group schemes over finite fields. 
As an application, we explain how to geometrize and categorify quasicharacters of  algebraic tori, abelian varieties and unipotent K-wound groups over connected commutative algebraic groups over non-Archimedean local fields that admit a Neron model locally of finite type,
\end{abstract}

>>>>

\begin{abstract}
We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
As an application, we find a category of sheaves whose isomorphism classes correspond to quasicharacters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields. 
In this geometrization of quasicharacters, our sheaves are local systems on
Greenberg transforms of locally finite type N\'eron models.
\end{abstract}
